Can BERT learn dialogue-specific phenomena? The case of laughter in dialogue act recognition.

### 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
typo

We use dialogue act recognition (DAR) as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on this task. DAR is the task of assigning a dialogue act tag to each utterance in the dialogue, according to dialogue act it performs.
Using this task we investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue. 
By looking at laughter, which is certainly missing in the stadnard pre-training corpus, we can determine whether the pre-training is used in the representation dialogue-specific features.

>>>>

We use dialogue act recognition (DAR) as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on this task. DAR is the task of assigning a dialogue act tag to each utterance in the dialogue, according to dialogue act it performs.
Using this task we investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue. 
By looking at laughter, which is certainly missing in the stadnard pre-training corpus, we can determine whether the pre-training is used in the representation of dialogue-specific features.
